Sequential rank agreement methods for comparison of ranked lists

### 2016-08-04 latex/superranker-manuscript.tex
Smårettelser

We start by defining the following cadlag function
\begin{align}
  N(p; d) = \sum_{s=1}^p 1\left(Q(R(X_s) \leq d) > 0\right), \quad p = 1,\ldots, P
\end{align}
which runs through the list elements in an arbitrary order and counts
how many list elements have a strictly positive probability to have
rank less than or equal to $d$ under the probability measure $Q$.
Note that the cardinality of the set $S(d)$ in equation
(\ref{eq:sumset}) is equal to the counting process evaluated at the last element: $|S(d)| = N(P;d)$.
The empirical counterpart of the counting process is given by
\begin{align}
  \widehat{N}_L(p; d) &= \sum_{s=1}^p 1\left( \frac{1}{L} \sum_{l=1}^L 1(R_l(X_s) \leq d) > 0\right)\\
        &= \sum_{s=1}^p 1\left(\widehat{Q}_L(R(X_s) \leq d) > 0\right)\nn.
\end{align}
The joint law of the sequence
$\{\widehat{N}_L(p;d)\}_{1\leq p \leq P}$ is completely determined by
the finite set of the jump times of $N(p;d)$. Since
$\{1(R_l(X_s) \leq d); l=1,\dots, L\}$ consists of independent and
identically Bernoulli distributed variables with expectation
$Q(R(X_s) \leq d)$ and finite variance it follows from the law of large numbers that
$\widehat{Q}_L(R(X_p) \leq d) \overset{P}{\longrightarrow} Q(R(X_p)
\leq d)$ for every $p$ and $d$ as $L \rightarrow \infty$. 
Therefore, we have
\begin{align}
  \sup_{d \in 1,\ldots,P}\sup_{p \in 1,\ldots, P} \left|\widehat{N}_L(p; d) - N(p; d)\right| = o_P(1).\label{eq:countingConv}
\end{align}

>>>>

We start by defining the following cadlag function
\begin{align}
  N(p; d) = \sum_{s=1}^p 1\left(Q(R(X_s) \leq d) > 0\right), \quad p = 1,\ldots, P
\end{align}
which runs through the list elements in an arbitrary order and counts
how many list elements that have a strictly positive probability to have
rank less than or equal to $d$ under the probability measure $Q$.
Note that the cardinality of the set $S(d)$ in equation
(\ref{eq:sumset}) is equal to the counting process evaluated at the last element: $|S(d)| = N(P;d)$.
The empirical counterpart of the counting process is given by
\begin{align}
  \widehat{N}_L(p; d) &= \sum_{s=1}^p 1\left( \frac{1}{L} \sum_{l=1}^L 1(R_l(X_s) \leq d) > 0\right)\\
        &= \sum_{s=1}^p 1\left(\widehat{Q}_L(R(X_s) \leq d) > 0\right)\nn.
\end{align}
The joint law of the sequence
$\{\widehat{N}_L(p;d)\}_{1\leq p \leq P}$ is completely determined by
the finite set of the jump times of $N(p;d)$. Since
$\{1(R_l(X_s) \leq d); l=1,\dots, L\}$ consists of independent and
identically Bernoulli distributed variables with expectation
$Q(R(X_s) \leq d)$ and finite variance it follows from the law of large numbers that
$\widehat{Q}_L(R(X_p) \leq d) \overset{P}{\longrightarrow} Q(R(X_p)
\leq d)$ for every $p$ and $d$ as $L \rightarrow \infty$. 
Therefore, we have
\begin{align}
  \sup_{d \in 1,\ldots,P}\sup_{p \in 1,\ldots, P} \left|\widehat{N}_L(p; d) - N(p; d)\right| = o_P(1).\label{eq:countingConv}
\end{align}
